### 2018-05-30 manuscript/data.tex
data new fig!

Over the releasing time period from \m{June to October} in 2015, 25481 individules (48\% females and 52\% males) were reached and \m{XXX} trips are collected. The majority of our 25481 volunteers contribute \m{XXX} trips.

@@

In the report (looking for some report), the penetration of mobile device is \m{XXX}, almost every XX people got a Mobile Phone in the urban. Figure~\ref{fig:data_age_edu} shows samples covering a wide range of all ages, dominately between 18 to 45. There is also a few records pertaining to individuals below the age of 18 or above 70. The distribution aligns to the fact that Shenzhen is a city where the majority is young people. According to the 2015 Annual Census Statistics report~\footnote{http://www.sztj.gov.cn/xxgk/tjsj/pcgb/201606/t20160614\_3697000.htm}, people aging 15-64 occupy 83.23\% and the median age is 31.5. Figure~\ref{fig:data_age_edu} gives the distribution of education levels, diverse from low to high.

>>>>

Over the releasing time period from \m{2016-11 to 2018-01}, 25481 individules (48\% females and 52\% males) were reached and \m{229155} trips are collected. The majority of our 25481 volunteers contribute \m{9} trips averagly.

@@

Figure~\ref{fig:data_age_edu} gives the distribution of age and education over the population. It shows that samples cover a wide range of all ages, dominately between 18 to 45. There is also a few records pertaining to individuals below the age of 18 or above 70. The distribution follows the fact that Shenzhen is a city where the majority is young people. According to the 2015 Annual Census Statistics report\footnote{http://www.sztj.gov.cn/xxgk/tjsj/pcgb/201606/t20160614\_3697000.htm}, people aging 15-64 occupy 83.23\% and the median age is 31.5. Figure~\ref{fig:data_age_edu} gives the distribution of education levels, ranging from low to high. The technical college and university dominates the education at the 61\% occupancy rate.

% In the report (looking for some report), the penetration of mobile device is \m{XXX}, almost every XX people got a Mobile Phone in the urban.
